%______________________________________________________________________________________________________________________
% @brief    based on LaTeX2e Resume by Kamil K Wojcicki
\documentclass[margin,line]{resume}

\usepackage{hyperref}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large{Michael Kocher}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    San Francisco, CA\hfill e-mail: michael.kocher@me.com\\\vspace{4.0mm}
    \hfill{\url{https://github.com/mpkocher}}\\\vspace{-9.0mm}

    % end Contact
    % end -----------------------------------------------

    
    % Education
    \section{\mysidestyle Education}

    \textbf{Ph.D. Material Science and Engineering} \\
    Arizona State University,  Tempe, AZ 85287 \hfill December 2008\\
    Thesis: \textsl{The Electronic Structure of Lithium Transition Metal Oxides}\vspace{2mm}\\
    \textbf{Bachelor of Science in Physics} \\
    Arizona State University,  Tempe, AZ 85287 \hfill April 2004\vspace{2mm}\\
    \textbf{Bachelor of Science in Chemistry}\\
    Arizona State University,  Tempe, AZ 85287 \hfill April 2004\\\vspace{-3mm}

    % end Education
    % end -----------------------------------------------



    % Tools and Frameworks
    \section{\mysidestyle Programming, Tools and Frameworks}

    \textbf{Languages and Technologies}: Scala, Python, PostgreSQL, MongoDB, R and Git\vspace{2mm}\\
                Experience with Scala, Akka, and Slick to drive scientific applications using an Agile process. MongoDB and SQL for database driven applications and experienced with object-oriented programming using
                Scala, Python and Ruby. Extensive experience with PBS, Slurm and SGE for running high-throughput computations on HPC systems. 8+ years of experience with Vienna
                \textsl{ab initio} Simulation Package (VASP) and Wien2k to compute properties of materials from first principles. Knowledgeable Bash for general scripting and system administration and R for data analysis.


  % End tools Frameworks
  % end -----------------------------------------------


   % Research Interests
    \section{\mysidestyle Research\\Interests}

    Data Processing and Analysis, High-throughput computing, workflows, data pipelines, HPC computing, \textsl{ab initio} materials science
    and chemistry, document based data storage (MongoDB), message queues, scientific gateways and RESTful interfaces for web driven scientific applications.

  % Research Interests 
  % end -----------------------------------------------
    
  % Professional Experience
  \section{\mysidestyle Professional\\Experience}
  \textbf{Senior Staff Engineer}\hfill June 2015 -- present\vspace{1mm}\\
     Pacific Biosciences, Menlo Park, CA\\\vspace{-3.0mm}
       \begin{list2}
       \item Secondary Analysis Infrastructure Tech Lead for the Sequel Release (SMRT Link 3.0) and member of the Architectural Review Board (ARB)
       \item Lead migration from Python/Java to Scala for maintainability (\href{https://github.com/PacificBiosciences/smrtflow}{smrtflow})
       \item Lead author for PacBio workflow engine (\href{https://github.com/PacificBiosciences/pbsmrtpipe}{pbsmrtpipe})
       \item Lead author for PacBio python common core library, \href{https://github.com/PacificBiosciences/pbcommand}{pbcommand} and the (internal) R companion, pbcommandr
   \end{list2}

     \textbf{Senior Scientist, Staff Engineer}\hfill December 2012 -- June 2015\vspace{1mm}\\
       Pacific Biosciences, Menlo Park, CA\\\vspace{-3.0mm}
   \begin{list2}
   \item Introduced a streaming Monoid-ish model for computing report metrics in \href{https://github.com/PacificBiosciences/pbreports}{pbreports} package to address scalability issues and keep memory usage approximately constant.
   \item Convienced and implemented core testing framework (pysiv) to enable pipeline testing. This framework was folded back into the pipeline engine (\href{https://github.com/PacificBiosciences/pbsmrtpipe}{pbsmrtpipe}) and is still currently in use.
   \item Contributed to converting pbpy mono-repo into smaller, more maintable and testable python packages.
   \item Pipeline feature development and maintenance of the SMRT Analysis 2.x workflow engine.
   \end{list2}

    \textbf{Postdoctoral Chemist Researcher} \hfill January 2009 -- April 2012\vspace{1mm}\\
		Lawrence Berkeley National Lab, Berkeley, CA\\
		Environmental Energy Technology Division. Advisor: Dr. Kristin Persson\\\vspace{-3.0mm}
    \begin{list2}
			\item Materials Project (\url{http://www.materialsproject.org}) lead developer and core database administrator. Designed NoSQL database driven scientific applications using Django and MongoDB
			\item Designed a distributed high-throughput workflow engine to perform MPI VASP calculations across several HPC centers
		  \item Performed calculation to investigate the role of Al substitution in Li transition metal oxides to understand Li diffusion, cation ordering and stability
		 \item Phonon calculations using \textsl{ab initio} quantum molecular dynamic simulations on $\mathrm{LiMnO_2}$ and $\mathrm{LiMn_2O_4}$ to determine thermal free energies and diffusion properties from first principles
     \item Performed electronic structure calculations on $\mathrm{LiC_x}$ and various Li transition metal oxides to understand the charge compensation mechanism during delithation
		\end{list2}

    \newpage
    % Graduate research
      \section{\mysidestyle Professional\\Experience (cont.)}
		\textbf{Graduate Research Assistant} \hfill September 2004 -- December 2008\vspace{1mm}\\
		Center for Solid State Science\\
Arizona State University Tempe\\
Advisor: Prof. Peter Rez\\\vspace{-1.5mm}
		\begin{list2}
			\item Electronic Structure of $\mathrm{LiMn_{1/2}Ni_{1/2}O_2}$ and $\mathrm{LiMn_{1/3}Ni_{1/3}Co_{1/3}O_2}$
			\item Electronic Structure calculations on $\mathrm{LiFePO_4}$ and $\mathrm{FePO_4}$
			\item Surface interactions of Aspartic and Glutamic Acid on $\mathrm{Ca(C_2O_4)(H_2O)}$
			\item Calculations on 5,7 defects in single wall carbon nanotubes
		\end{list2}

    % undergraduate research

		\textbf{Undergraduate Research Assistant} \hfill August 2001 -- August 2004\vspace{1mm}\\
		Center for Solid State Science\\
Arizona State University Tempe, AZ\\
Advisor: Prof. Andrew Chizmeshya\\\vspace{-1.5mm}
		\begin{list2}
			\item Performed calculations of $\mathrm{MgCO_3}$ and $\mathrm{Mg_2SiO_4}$ to determine elastic constants and free energies to understand chemical reactions in mineral sequestration of $\mathrm{CO_2}$
		 \item Spin polarized calculation to determine the enthalpy of mixing for $\mathrm{Mg_{1-x}Fe_{x}CO_{3}}$ solid solution to understand the effect of Fe impurities in serpentine on the sequestration process.
		 \item Phonon calculations using quantum molecular dynamic simulations on $\mathrm{MgCO_3}$ and $\mathrm{Mg_2SiO_4}$ to determine thermal free energies from first principles
		\end{list2}
		
    % Undergrad Research
		\textbf{Undergraduate Research Assistant} \hfill May 2002 – August 2004\vspace{1mm}\\
		Center for Solid State Science\\
Arizona State University Tempe, AZ\\
Advisor: Prof. Peter Rez\\\vspace{-1.5mm}
		\begin{list2}
			\item Electron Energy Loss Spectroscopy calculations of $\mathrm{SrTiO_3}$ and $\mathrm{LaTiO_3}$ from \textsl{ab initio} methods
			\item Calculations of surface energies of $\mathrm{Ca(C_2O_4)(H_2O)}$ and $\mathrm{Ca(C_2O_4)(H_2O)_2}$
			\item Role of acetylene on Ni (110) and (110) and Ni on graphene sheets for understanding of carbon nanotube formation
		\end{list2}
		
    % Undergrad Research
		\textbf{Undergraduate Research Assistant} \hfill August 2000 - May 2001\vspace{1mm}\\
		Department of Chemistry\\
Arizona State University Tempe, AZ\\
Advisor: Prof. Tim Steimle\\\vspace{-1.5mm}
		\begin{list2}
		\renewcommand{\labelitemi}{$\star$}
		\item Assisted in High resolution Spectroscopy experiments
		\item Maintenance of laboratory apparatus
		\item Programming of EEPROM Pic devices
		\end{list2}

  % Professional Experience
    % end -----------------------------------------------

      % Awards ----------------------------------------------------------------
    \section{\mysidestyle Awards}
    LBNL Spot Prize: ``For outstanding and inspiring
      work on the Materials Project'' \hfill January 2012\vspace{2mm}\\
    Top Prize in the LBNL 2010 Mobility Contest: \hfill February 2010\\
      ``Mobility Materials Genome: iPhone app to
       accelerate materials design process''

  % end Awards
  % end -----------------------------------------------

  % Selected Publications ------------------------------------------------
  \section{\mysidestyle Selected Publications}
    M. Kocher and K. Persson, "Li Mobility and the Electronic Structure of $\mathrm{LiMn_{1/3}Ni_{1/3}Co_{1-x}Al_{x}O_{2}}$ Determined from First-Principles" \textsl{Physical Review B} (submitted)\vspace{2mm}\\
    S. Miao, M. Kocher, P. Rez, B. Fultz, R. Yazami, and C. C. Ahn, "Local electronic structure of olivine phases of $\mathrm{Li_xFePO_4}$", \textsl{The Journal of Physical Chemistry A}, vol.111, pp.4242–7, May (2007).\vspace{2mm}\\
    S . Miao, M. Kocher, P. Rez, B. Fultz, Y. Ozawa, R. Yazami, and C. Ahn, "Local electronic structure of layered $\mathrm{Li_xNi_{0.5}Mn_{0.5}O_2}$ and $\mathrm{Li_{x}Ni_{1/3}Mn_{1/3}Co_{1/3}O_2}$", \textsl{Journal of Physical Chemistry B}, vol. 109, no. 49, pp. 23473–23479 (2005).\vspace{2mm}\\
    M.P. Kocher, D.A. Muller and P. Rez,, "The Oxygen K Edge in Strontium Titanate and Lanthanum Titanate", \textsl{Microscopy and Microanalysis}, (suppl. 2), 9, 842 (2003).\vspace{2mm}\\
    A. V. G. Chizmeshya, M. J. McKelvy, G. Wolf, M. Kocher, D. Gormley, "Quantum Simulations Studies of Olivine Mineral Carbonation", \textsl{Proc. 28th International Technical Conference on Coal Utilization   \& Fuel Systems} 319-330 (2003).

   \newpage
		\section{\mysidestyle Conference Presentations and
                  Posters}
                ``Using Python to Accelerate Materials Design'',
                Michael Kocher, Dan Gunter and Shreyas Cholia, PyCon,
                Santa Clara, CA March (2012)\vspace{2mm}\\
		``Using MongoDB for Materials Discovery'' Michael
                Kocher and Dan Gunter, MongoSV, Santa Clara, CA December (2011)\vspace{2mm}\\
                ``The Effect of Al Substitution in Lithium Transition Metal Oxides from First-principles'' Michael Kocher, Kristin A. Persson and Quentin M. Ramasse. Materials Research Society Spring Meeting, San Francisco, CA April (2010)\vspace{2mm}\\
		``Does Ni change its charge state in $\mathrm{Li(Mn_{0.5}Ni_{0.5})O_2}$ cathode materials?'' Peter Rez and Michael Kocher. 208 Electrochemical Society Meeting, Los Angeles, California, October (2005) \vspace{2mm}\\
		``Local Electronic Structure of Layered $\mathrm{Li_{x}Mn_{1/3}Ni_{1/3}Co_{1/3}O_{2}}$'' Brent Fultz, Shu Miao, Michael Kocher, Peter Rez, Yasuroni Ozawa, Rachid Yazami, and Channing Ahn. 208 Electrochemical Society Meeting, Los Angeles, California, October (2005) \vspace{2mm}\\

		``$\mathrm{CO_2}$ Mineral Carbonation Processes in
                  Olivine Feedstock: Insights from the Atomic Scale
                  Simulation'' Andrew V.G. Chizmeshya, Michael J.
                McKelvy, Deirdre Gormley, Michael Kocher, Ryan Nunez,
                Young-Chul Kim and Ray Carpenter, Proc. 29th
                International Technical Conference on Coal Utilization
                and Fuel Systems, Clearwater, Florida, April (2004)
                \vspace{2mm}\\
		``Exploration of the Role of Heat Activation in Enhancing Serpentine Carbon Sequestration Reactions'' Michael J. McKelvy, Andrew V.G. Chizmeshya, Jason Diefenbacher, George Wolf, Brandon Doss, Deirdre Gormley, Michael Kocher, and Hamdallah Bearat, Proc. 29th International Technical Conference on Coal Utilization and Fuel Systems, Clearwater, Florida, April (2004)\vspace{2mm}\\
    %__________________________________________________________________________________________________________________
                \section{\mysidestyle Workshops}
		Summer School of Computational Material Science \hfill July 2006\\
		Ab Initio Molecular Dynamics Simulation Methods in Chemistry\\
		University of Illinois Urbana-Champaign\vspace{-2mm}\\\vspace{-2mm}

		International Center for Materials Research Summer School\hfill August 2005\\
		First Principles Calculations for Condensed Matter and Nanoscience\\
		University of California Santa Barbara\\

  % Pubs
  % end -----------------------------------------------


    %__________________________________________________________________________________________________________________
    % Referees
		\section{\mysidestyle References}
		{\sl Available on request.}
%______________________________________________________________________________________________________________________
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
